Estimating the incidence of SARS-CoV-2 from prevalence data

### 2023-05-26 main.tex
Follow UoC formatting rules

\documentclass[a4paper]{report}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

@@

\title{Estimating the incidence of SARS-CoV-2 from prevalence data}
\author{Joshua Blake}
\date{\today}

@@

@@

@@

\chapter{Survival analysis with perfect testing} \label{perf-test}

@@

\todo[inline]{Add some descriptive figures e.g. those in ~/COVID/ons-incidence/duration_estimation/reproducible-sims/reports/simulation-studies.pdf}

>>>>

\documentclass[a4paper,12pt,custombib,times]{PhDThesisPSnPDF} % add print option for printing
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

@@

\title{Estimating the incidence of SARS-CoV-2 from prevalence data}
\author{Joshua Blake}
\supervisor{Prof.~D.~De Angelis \newline Dr.~P.~Birrell}
\date{\today}
\dept{MRC Biostatistics Unit}
\university{University of Cambridge}
\crest{\includegraphics[width=0.45\textwidth]{University_Crest_Long}}
\college{Jesus College}
\collegeshield{\includegraphics[width=0.2\textwidth]{jesus}}
\degreetitle{Doctor of Philosophy}

@@

\frontmatter

@@

\begin{declaration}
    This thesis is my own work and contains nothing which is the outcome of work done in collaboration with others except as specified in the text and Acknowledgements.
    It is not substantially the same as any work that has already been submitted before for any degree or other qualification except as declared in the preface and specified in the text.
    The thesis contains no more than 60,000 words (excluding figures, photographs, tables, appendices, and bibliography).
\end{declaration}

\begin{acknowledgements}      
    \todo[inline]{Acknowledgements here}    
\end{acknowledgements}

\tableofcontents

\listoffigures

\mainmatter

@@

@@

\todo[inline]{Add some descriptive figures e.g. those in \url{~/COVID/ons-incidence/duration_estimation/reproducible-sims/reports/simulation-studies.pdf}}
